\documentclass[10pt]{article}
% Syllabus: 12.3.1, 12.3.2, 12.4.1.1, 13.2.1, 15.1.1
% Assignment: 12.3.2, 12.4.1.1, 13.2.1, 15.1.1

% Note that 12.3.1 and 12.3.2 are the exercises at the end of section 12.3 that are not labeled in
% the text.

% Due Feb. 10
\usepackage{bs-zed}

\begin{document}
\title{the way of Z \\ Chapters 12, 13 \& 15 Problems}
\author{Ben Straub}
\maketitle

\section{Exercise 12.3.1}
\begin{quote}
  {\it
    Expand $\forall Editor | Init @ EOF$.
  }
\end{quote}
Read aloud, this says that for all Editor states where Init holds, EOF holds as well. To verify
this, we just need to expand out $Init \land EOF$ in the $Editor$ context and see if there are any
contradictions.

For reference:
\begin{spec}
%   \begin{zed}
%     [CHAR] \also
%     TEXT == \seq CHAR
%   \end{zed}
%   \begin{axdef}
%     maxsize : \num
%     \where
%     maxsize \leq 65535
%   \end{axdef}
  \begin{schema}{Editor}
    left, right : TEXT \where \#(left \cat right) \leq maxsize
  \end{schema}
  \begin{schema}{Init}
    Editor \where left = right = \langle \rangle
  \end{schema}
  \begin{schema}{EOF}
    Editor \where right = \langle \rangle
  \end{schema}

  Given these, the expression expands to:

  \begin{zed}
    \forall left,right : TEXT | (\#(left \cat right) \leq maxsize) \land (left = right = \langle \rangle) @ \\
    \t1 right = \langle \rangle
  \end{zed}
\end{spec}



\section{Exercise 12.3.2}
\begin{quote}
  {\it
    What does $S\_Division$ say about $status$ when the $DivideByZero$ condition does not occur?
  }
\end{quote}

\begin{spec}
  \begin{schema}{S\_Division}
    T\_Division \\
    status : STATUS
    \where
    DivideByZero \iff status = error
  \end{schema}
\end{spec}
The expression $a \iff b$ means $(a \land b) \lor (\lnot a \land \lnot b)$.  So when $S\_Division$
says that $DivideByZero \iff status = error$, this means
\[ (DivideByZero \land status = error) \lor
   (\lnot DivideByZero \land status \neq error) \]
That second clause, since $STATUS$ has only two values, really says that $status = ok$.


\section{Exercise 12.4.1.1}
\begin{quote}
  {\it
   What is the precondition of $ForwardTwo$? 
  }
\end{quote}

We could expand out $ForwardTwo$ explicitly using primes and double primes:

\begin{spec}
  \begin{schema}{ForwardTwo}
    left, right, left', right', left'', right'' : TEXT \\
    ch?, ch?' : CHAR \where
    \#(left \cat right) \leq maxsize\\
    \#(left' \cat right') \leq maxsize\\
    \#(left'' \cat right'') \leq maxsize\\
    ch? = ch?' = right\_arrow \\
    right \neq \langle \rangle \\
    right' \neq \langle \rangle \\
    left' = left \cat \langle head(right)\rangle \\
    right' = tail(right) \\
    left'' = left' \cat \langle head(right')\rangle \\
    right'' = tail(right') \\
  \end{schema}
\end{spec}
The most interesting precondition is $right' \neq \langle \rangle$.  This means that $\#right \geq
2$, or our editor will crash.

As a side note, the $ch? = ch?' = right\_arrow$ restriction is a bit confusing.  It almost seems as
if Z is encouraging us to separate input classification (recognizing which key was pressed) from
state transitions (moving the cursor).  Combining the two gives you this wierd predicate where a
transition with no middle state requires that the same key be pressed twice.



\section{Exercise 13.2.1}
\begin{quote}
  {\it
    Define the operation $Next$ that advances a $Date$ by one day.
  }
\end{quote}

I'm sure there's a more succinct way to write it.

\begin{spec}
  \begin{schema}{Next}
    \Delta Date
    \where
    (month = 12 \land day = 31 \land \\
    \t1 day' = 1 \land month' = 1 \land year' = year + 1) \lor \\
    (leap\ year \land day = 28 \land month = 2 \land \\
    \t1 day' = 29 \land month' = month \land year' = year) \lor \\
    (Feb29 \land \\
    \t1 day' = 1 \land month' = 3 \land year' = year) \lor \\
    (day = days\ month \land \\
    \t1 day' = 1 \land month' = month + 1 \land year' = year) \lor \\
    (day' = day + 1 \land month' = month \land year' = year)
  \end{schema}
\end{spec}
This covers the year-end, entry and exit for February 29, every other month-end, and finally all the
other days.  I'm not very happy with it, though.



\section{Exercise 15.1.1}
\begin{quote}
  {\it
    Equality $=$, greater than $>$, and less than $<$ are all transitive. Is inequality $\neq$
    transitive as well?
  }
\end{quote}

No.  If it were, $2 \neq 5 \neq 2$ would imply $2 \neq 2$.


\end{document}